---
title: "RMarkdown to redmine (textile format) converter"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
```

## Overview

The converter supports:

* Different levels of headings
* Plain text
* Code chunks
* `Inline code/monospace`
* [Inline links](https://www.github.com)
* Lists
    1. Nested lists
    1. Including different styles
        * No matter how deeply they are nested
            * At all
* Figures
* Tables
* Horizontal rules (separators)
* **Bold** and *italic* formatting

## Working with figures

How to use this script if your RMarkdown includes figures:

1. Make sure your RMarkdown and rmd2redmine.sh are in the same directory
1. Your script must store figures in `./pdfs/`
1. The directory must also contain a folder named `pngs`. This is where the redmine-compatible pngs will be stored.
1. Figures must follow the naming convention `[name of script][counter].pdf`, e.g., my_analysis_01.pdf, but you may add a description before the counter
1. The output of your RMarkdown must be an html document
1. When your RMarkdown ensures all the above, call `$ ./rmd2redmine.sh [name of script].Rmd` from the system terminal. The script will
    1. Knit the document to html
    1. Convert the figures from PDF to PNG
    1. Create a new .redmine file from the contents of the html file
1. Now you only need to copy-paste the .redmine contents into your redmine update and upload the PNGs

## Examples

### Figures

```{r example-plot, echo=FALSE}
ggplot(iris, aes(Sepal.Width, Petal.Width, col = Species)) +
  geom_point(size = 2) +
  ggtitle('Example figure') +
  theme(text = element_text(size = 20))
```

### Tables

This table was typed manually in RMarkdown syntax. Blank cells intentionally left blank.

| Lorem | ipsum |
|---|---|
|dolor|sit|
|amet||
|consetetur|sadipscing|
||elitr|

---

Whereas this table is contained in a code chunk.

```{r example-table}
# Here is an example code chunk with output

head(iris)
```

---

If you don't like code chunks, but like automation, pass tabular data to knitr::kable().

```{r kable_demo}
# This code chunk could also have been hidden so that only the output is displayed.
# To achieve that, use the chunk option include=FALSE

knitr::kable(head(iris))
```


