---
title: "RMarkdown to redmine (textile format) converter"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
```

## Overview

The converter supports:

* Different levels of headings
* Plain text
* Code chunks
* `Inline code/monospace`
* [Inline links](https://www.github.com)
* Lists
    1. Nested lists
    1. Including different styles
* Figures (are now handled automatically, no need to even save them)
* Tables
* Horizontal rules (separators)
* **Bold** and *italic* formatting

## Examples

### Figures

Here's a figure based on iris.

```{r example-plot-1, echo=FALSE}
ggplot(iris, aes(Sepal.Length, Petal.Length, col = Species)) +
  geom_point(size = 2) +
  ggtitle('Example iris') +
  theme(text = element_text(size = 20))
```

And here is one based on mtcars.

```{r example-plot-2, echo=FALSE}
ggplot(mtcars, aes(mpg, hp, col = factor(gear))) +
  geom_point(size = 2) +
  labs(col = "gear") +
  ggtitle('Example mtcars') +
  theme(text = element_text(size = 20))
```

### Tables

This table was typed manually in RMarkdown syntax. Blank cells intentionally left blank.

| Lorem | ipsum |
|---|---|
|dolor|sit|
|amet||
|consetetur|sadipscing|
||elitr|

---

Whereas this table is contained in a code chunk.

```{r example-table}
# Here is an example code chunk with output

head(iris)
```

---

If you don't like code chunks, pass tabular data to `knitr::kable()`.

```{r kable_demo}
# This code chunk could also have been hidden so that only the output is displayed.
# To achieve that, use the chunk option include=FALSE

knitr::kable(head(iris))
```


